Evaluation of probabilistic photometric redshift estimation approaches for \boldblue{ \textsc{The Rubin Observatory Legacy Survey of Space and Time} (LSST)}

### 2020-06-12 paper/tex/introduction.tex
fix minor typo

\boldblue{In currently available spectroscopic training sets systematic incompleteness, particularly at faint magnitudes, and incorrectly assigned redshifts are a harrowing problem.  Certain subpopulations can potentially fail to yield secure redshifts, given limited wavelength coverage.  Alternately, redshifts may be  incorrectly assigned for certain populations due to misidentification of spectral features.  These missing or misidentified populations would yield training sets that are not representative of the true underlying galaxy population, which can bias redshift estimates well beyond the levels required for upcoming analyses.  Characterizing and mitigating these problems will be a major undertaking which we will cover in future papers, as discussed briefly in \S,\ref{sec:futureexperiments}.  Before taking on this very complex issue, however, we must first investigate a more fundamental one: how do current methods perform in the presence of representative data?}

>>>>

\boldblue{In currently available spectroscopic training sets systematic incompleteness, particularly at faint magnitudes, and incorrectly assigned redshifts are a harrowing problem.  Certain subpopulations can potentially fail to yield secure redshifts, given limited wavelength coverage.  Alternately, redshifts may be  incorrectly assigned for certain populations due to misidentification of spectral features.  These missing or misidentified populations would yield training sets that are not representative of the true underlying galaxy population, which can bias redshift estimates well beyond the levels required for upcoming analyses.  Characterizing and mitigating these problems will be a major undertaking which we will cover in future papers, as discussed briefly in \S \ref{sec:futureexperiments}.  Before taking on this very complex issue, however, we must first investigate a more fundamental one: how do current methods perform in the presence of representative data?}
